UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-21 paper/paper.tex
updates

@@

\subsection{Intersection points}
\myparagraph{Scheme1}
Intersection points:
Light/medium : 17
Medium/heavy : 13
Light / heavy : 16
\myparagraph{Scheme2}
Intersection points:
Light/medium : Never (surprisingly medium is never cheaper than light)
Medium/heavy : 6
Light / heavy : 14

\section{Transform initial Google data schema to below per day}

Schema after transformation (splitted per day)
        1,machine ID,INTEGER,YES
        2,uptime (how many hours machine is on),INTEGER,YES
        3,uptime based on summarized task time,INTEGER,YES
        4,total CPU usage,INTEGER,YES
        5,CPU capacity, INTEGER, YES
        6,total assigned memory usage,FLOAT,NO
        7,total maximum memory usage,FLOAT,NO
        8,MEMORY capacity,FLOAT,YES
        9,NUMBER of tasks per machine per day

>>>>

TO BE REWRITTEN!

@@

\subsection{Intersection points}

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l | l |}
    \hline
    & \textbf{Scheme 1} & \textbf{Scheme 2} \\
    \hline
    light/medium & 17 & never \\
    \hline
    light/heavy & 16 & 6 \\
    \hline
    medium/heavy & 13 & 14 \\
    \hline
    \end{tabular}
\end{center}
\caption{Intersection points for Scheme 1 and Scheme 2}
\label{tab:intersection_points}
\end{table}

\begin{figure}[H]
  \includegraphics[width=\linewidth]{figures/m2_4xlarge}
  \caption{\textit{cph} results for Amazon AWS m2.4xlarge reserved instance rented for 1 year~\cite{AWS:light}~\cite{AWS:medium}~\cite{AWS:heavy}}
  \label{fig:m2_4xlarge}
\end{figure}

\section{Google trace data schema transformation}

We used machine and tasks data for further evaluation. Machine information regarding ID and capacity can be found in machine events  .

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l |}
    \hline
    & \textbf{Column name} \\
    \hline
    1 & timestamp\\
    \hline
    2 & machine id\\
     \hline
    3 & event type\\
     \hline
    4 & platform id\\
     \hline
    5 & capacity: CPU\\
     \hline
    6 & capacity: memory\\
    \hline
    \end{tabular}
\end{center}
\caption{Machine events table schema from Google trace}
\label{tab:machine_events}
\end{table}

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l |}
    \hline
    & \textbf{Column name} \\
    \hline
    1 & start time of the measurement period\\
    \hline
    2 & end time of the measurement period\\
     \hline
    3 & job ID\\
     \hline
    4 & task index\\
     \hline
    5 & machine ID \\
     \hline
    6 & mean CPU usage rate \\
    \hline
    7 & canonical memory usage\\
    \hline
    8 & assigned memory usage\\
    \hline
    9 & unmapped page cache memory usage\\
    \hline
    10 & total page cache memory usage\\
    \hline
    11 & maximum memory usage\\
    \hline
    12 & mean disk I/O time\\
    \hline
    13 & mean local disk space used\\
    \hline
    14 & maximum CPU usage\\
    \hline
    15 & maximum disk IO time\\
    \hline
    16 & cycles per instruction (CPI)\\
    \hline
    17 & memory accesses per instruction\\
    \hline
    18 & sample portion\\
    \hline
    19 & aggregation type \\
    \hline    
    20 & sampled CPU usage\\
    \hline
    \end{tabular}
\end{center}
\caption{Machine events table schema from Google trace}
\label{tab:task_events}
\end{table}

Transformation to below schema. 
- uptime per day
- total CPU usage per day
- total memory usage per day
- total number of tasks per day

\begin{lstlisting}
Schema after transformation (splitted per day)
        1,machine ID,INTEGER,YES
        2,uptime
        4,total CPU usage,INTEGER,YES
        5,CPU capacity, INTEGER, YES
        6,total assigned memory usage,FLOAT,NO
        8,MEMORY capacity,FLOAT,YES
        9,NUMBER of tasks per machine per day
\end{lstlisting}

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l |}
    \hline
    & \textbf{Column name} \\
    \hline
    1 & timestamp\\
    \hline
    2 & machine id\\
     \hline
    3 & event type\\
     \hline
    4 & platform id\\
     \hline
    5 & capacity: CPU\\
     \hline
    6 & capacity: memory\\
    \hline
    \end{tabular}
\end{center}
\caption{Machine events table schema from Google trace}
\label{tab:new_schema}
\end{table}

~\cite{test}
